---
title: "pilot EEG ERP analysis"
author: "Christopher"
date: "17 3 2025"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
---



```{r load_package, message = FALSE, warning = FALSE}
library(lme4)
library(readxl)
library(tidyverse)
library(data.table)
library(tidyverse)
library(afex)
library(broom)
library(apa)
library(kableExtra)
library(lmerTest)
library(pbkrtest)
library(effects)
library(visreg)
library(sjPlot)
library(broom.mixed)
library(pander)
library(mediation)
library(multcomp)
library(multcompView)
library(magrittr)
library(multipanelfigure)
library(ggbeeswarm)
library(lsmeans)
library(BayesFactor)
library(ggpubr)
library(gpairs)
library(DescTools)
library(cowplot)
library(ggpol)
library(psych)

library(ggdist)

source('C:/Users/psy05cvd/Dropbox/work/R-statistics/general_functions/RainCloudPlots/tutorial_R/R_rainclouds.R')





# broad cluster
# CSD based normalized to pre-cue baseline in %
# 
DATAPath_ERP = "data_in/ERP_pilotdata_LargeLateralClust_03-31-2025_13-41.csv"
DATAPath_SSVEP = "data_in/FFT_SSVEP_pilotdata_04-01-2025_08-48.csv"





options(scipen=1, digits=5)
```
<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>


## Prepare data  
<br>  

1.  Read in data: 
    + `r DATAPath`
    
<br>  

```{r load_data,results = "hide", fig.show = "hide", warning = FALSE}
# read in data
DataIn_ERP <- read_delim(DATAPath_ERP, delim = ';') %>%
  mutate(participants = as.factor(participants)) %>%
  mutate(time_label = factor(time_label, levels = c("tracking","retention","probe"), ordered = T))
head(DataIn_ERP)
str(DataIn_ERP)

DataIn_SSVEP <- read_delim(DATAPath_SSVEP, delim = ';') %>%
  mutate(participants = as.factor(participants)) %>%
  mutate(time_label = factor(time_label, levels = c("tracking","retention","probe"), ordered = T))

# unique(DataIn_ERP$participants)


```


## Illustrate behavioral data for main experiment for different conditions

<br>  

```{r plot_data_avg, results = "hide",  fig.height=2, fig.width=4, warning = FALSE}

dat2plot <- DataIn_ERP %>%
  dplyr::select(-elecs)%>%
  pivot_wider(names_from = "elec_label", values_from = "amplitude")%>%
  mutate(`contra-ipsi` = `contra`-`ipsi`)%>%
  pivot_longer(cols=`ipsi`:`contra-ipsi`, names_to = "signal", values_to = "amplitude")%>%
  group_by(participants, con_label3, time, time_label, signal) %>%
  summarise(amplitude = mean(amplitude))%>%
  filter(signal == "contra-ipsi")


# plot ERP components
theme_set(theme_bw())
ggplot(dat2plot, aes(x = con_label3, y = amplitude, fill = con_label3)) +
  geom_hline(yintercept = 0, color = "grey20", size = 0.5) +
  geom_line(aes(group = participants),colour = "grey60",alpha = 1,size =1) +
  geom_beeswarm(aes(color = con_label3, x = con_label3,group = con_label3), cex=1.5, size = 3.5,alpha=1,fill="grey40",shape=21)+
  stat_summary(fun.y=mean, aes(ymin=..y.., ymax=..y.., color = con_label3), geom='errorbar', width=1.1, size=1.5) +
  facet_wrap(~time_label) +
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  ylab(expression(paste("amplitude in ", mu, "V/cm²")))
  # theme(axis.title.x=element_blank(),
  #       axis.text.x=element_blank(),
  #       axis.ticks.x=element_blank())




```



## Display behavioral data for main experiment numerically

<br>  

```{r disp_data_avg, warning = FALSE}
dat2plot <- DataIn_ERP %>%
  group_by(participant, con3label) %>%
  mutate(event_num = n())%>%
  group_by(participant, con3label,event_response_type)%>%
  summarise(
    RT_Mean=mean(event_response_RT),
    RT_STD=sd(event_response_RT),
    N=n(),
    Rate= (n()/first(event_num))*100
    ) %>%
  ungroup()%>%
  complete(participant, con3label, event_response_type,
           fill=list(RT_Mean=NaN, RT_STD=NaN, RT_resp=NaN, N=0, Rate=0))

dat2plot  %>%
  group_by(event_response_type, con3label)%>%
  summarise(N = n(), mean_RT = mean(RT_Mean), std_RT = sd(RT_Mean), mean_rate = mean(Rate), std_rate = sd(Rate)) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3,3), caption = c("descriptives of behavioral measures")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```



## Display behavioral data for pre-cue experiment numerically

<br>  

```{r disp_data_avg_precue, warning = FALSE}
dat2plot <- DataIn %>%
  group_by(participant) %>%
  mutate(event_num = sum(precue_eventnum))%>%
  group_by(participant,precue_event_response_type) %>%
  filter(precue_event_response_type %in% c("hit","error","miss"))%>%
  summarise(
    RT_Mean=mean(precue_event_response_RT),
    RT_STD=sd(precue_event_response_RT),
    N=n(),
    Rate= (n()/first(event_num))*100
    ) %>%
  ungroup()%>%
  complete(participant, precue_event_response_type,
           fill=list(RT_Mean=NaN, RT_STD=NaN, RT_resp=NaN, N=0, Rate=0))

dat2plot  %>%
  group_by(precue_event_response_type)%>%
  summarise(N = n(), mean_RT = mean(RT_Mean), std_RT = sd(RT_Mean), mean_rate = mean(Rate), std_rate = sd(Rate)) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3,3), caption = c("descriptives of pre cue behavioral measures")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))

```


## Illustrate single trial RT data for main experiment for different conditions

<br>  

```{r plot_data_singletrial_RT, results = "hide",  fig.height=4, fig.width=3.5, warning = FALSE}

dat2plot <- DataIn %>%
  filter(event_response_type %in% c("hit"))


plot1 <-
  ggplot(dat2plot, aes(
    x = event_response_RT, 
    fill = con3label, fill_ramp = after_stat(abs(x)), 
    color_ramp = after_stat(-dnorm(x, 0, 2))
  )) +
  stat_slab(
    height = 2, color = "gray15",
    expand = TRUE, trim = TRUE,
    fill_type = "segments",
    show.legend = FALSE,
    position = position_dodgejust(0.3),
  )+
  theme(axis.text.y=element_blank(),axis.ticks.y=element_blank(), axis.title.y = element_blank())+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(), axis.title.x = element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83")) +
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))+
  xlim(c(100, 1500))

plot2 <-
  ggplot(dat2plot, aes(
    x = event_response_RT, 
    fill = con3label
  )) +
  stat_pointinterval(position = position_dodge(width = .4, preserve = "single"), 
                     aes(color=con3label), .width= c(.68, .95)) +
  theme(axis.text.y=element_blank(),axis.ticks.y=element_blank(), axis.title.y = element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(name="RT in ms", breaks=c(200,400,600,800,1000,1200,1400), labels=waiver(), limits=c(100,1500))+
  scale_fill_manual(values=c("#F1831A", "#293C4A", "#198A83")) +
  scale_color_manual(values=c("#F1831A", "#293C4A", "#198A83"))
  


# cowplot::plot_grid(plot1, plot2, plot3, ncol = 3,labels = "AUTO")
plotttitle <- ggdraw() + draw_label("RT for hits in ms", fontface='bold')
plotplots <- ggarrange(plot1, plot2, nrow = 2, align = "v", heights =c(4,2), common.legend = TRUE)
g<-ggarrange(plotttitle, plotplots, nrow = 2, heights=c(0.1, 1))

print(g)
# ggsave(filename = "figures/RT_distribution_validityeffects.eps", width = 5, height = 3.5,
#        plot = print(g))

```

## Statistical analysis

### ANOVA models
### linear mixed models

#### test RT, Hitrate, error rate and miss rate differences between conditions

<br> 

```{r lme_RT_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
dat2plot <- DataIn %>%
  group_by(participant, con3label) %>%
  mutate(event_num = n())%>%
  group_by(participant, con3label,event_response_type)%>%
  summarise(
    RT_Mean=mean(event_response_RT),
    RT_STD=sd(event_response_RT),
    N=n(),
    Rate= (n()/first(event_num))*100
    ) %>%
  ungroup()%>%
  complete(participant, con3label, event_response_type,
           fill=list(RT_Mean=NaN, RT_STD=NaN, RT_resp=NaN, N=0, Rate=0))%>%
   rename(condition = con3label)

dat2plot %>%
  group_by(event_response_type)%>%
  nest()%>%
  mutate(stats= purrr::map(data, ~broom::tidy(
    anova(aov_ez(id="participant", dv = "Rate", data = ., within = "condition"))
  ))) %>%
  dplyr::select(-data) %>%
  unnest()%>%
  ungroup()%>%
  mutate(
    `p.value` = cell_spec(ifelse(round(`p.value`,4)<.001,"< .001",round(`p.value`,4)), 
                        color = ifelse(is.nan(`p.value`),"blue", ifelse(`p.value` < .05, "green", "red")),
                        bold = ifelse(is.nan(`p.value`),F, ifelse(`p.value` < .05, T,F)),
                        align = "center")
  ) %>%
  dplyr::select(event_response_type, `num.Df`, `den.Df`, MSE, `statistic`, ges, `p.value`) %>%
  rename(`F` = `statistic`) %>%  
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA for rates | rates ~ condition")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


StatsOut <- dat2plot %>%
  filter(event_response_type %in% c("hit","error")) %>%
  aov_ez(id="participant", dv = "RT_Mean", data = ., within = c("condition","event_response_type"), 
         include_aov = afex_options("include_aov"))

StatsOut%>%
  .$anova %>% 
  mutate(factor = rownames(.))%>% 
  mutate( 
    `Pr(>F)` = cell_spec(ifelse(round(`Pr(>F)`,4)<.001,"< .001",round(`Pr(>F)`,4)), 
                        color = ifelse(is.nan(`Pr(>F)`),"blue", ifelse(`Pr(>F)` < .05, "green", "red")), 
                        bold = ifelse(is.nan(`Pr(>F)`),F, ifelse(`Pr(>F)` < .05, T,F)), 
                        align = "center") 
  ) %>% 
  dplyr::select(`num Df`, `den Df`, MSE, `F`, ges, `Pr(>F)`) %>% 
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("repeated measures ANOVA | for hits and errors only | dv = RT in ms")) %>% 
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 6)) 
```


 dat2plot2 <- DataIn2 %>%
  mutate(`FA_all`= FA + `FA_proper`)%>%
  # dplyr::select(-FA)%>%
  dplyr::select(-FA_all)%>%
  pivot_longer(c(-subject ),names_to = "FA_type", values_to = "number")%>%
  filter(FA_type=='FA_proper' | FA_type=='FA')


dat2plot <- DATA_Trials %>%
  group_by(participant,colorlum)%>%
  summarise(RT_Mean=mean(RT,na.rm=TRUE),RT_STD=sd(RT,na.rm=TRUE),Hitrate=(sum(response=='hit')/n())*100)

dat2plot2 <- DataIn2 %>%
  mutate(`FA_all`= FA + `FA_proper`)%>%
  # dplyr::select(-FA)%>%
  dplyr::select(-FA_all)%>%
  rename(participant=subject)

dat2plot_all <- merge(dat2plot,dat2plot2) %>%
  mutate(
    d_prime = qnorm(Hitrate/100)-qnorm(FA_proper_rate),
    c = -0.5*(qnorm(Hitrate/100)+qnorm(FA_proper_rate))
  )


# # statisticical analysis ANOVA
# StatsOut <- dat2plot_all %>%
#   aov_ez(id="participant", dv = "RT_Mean", data = ., between = c("colorlum"), include_aov = afex_options("include_aov")) 
#
# StatsOut%>%
#   .$anova %>% -->
#   mutate(factor = rownames(.))%>% -->
#   mutate( -->
#     `Pr(>F)` = cell_spec(ifelse(round(`Pr(>F)`,4)<.001,"< .001",round(`Pr(>F)`,4)), -->
#                         color = ifelse(is.nan(`Pr(>F)`),"blue", ifelse(`Pr(>F)` < .05, "green", "red")), -->
#                         bold = ifelse(is.nan(`Pr(>F)`),F, ifelse(`Pr(>F)` < .05, T,F)), -->
#                         align = "center") -->
#   ) %>% -->
#   dplyr::select(`num Df`, `den Df`, MSE, `F`, ges, `Pr(>F)`) %>% -->
#   kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), caption = c("ANOVA | dv = RT in ms")) %>% -->
#   kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 6)) -->


# RT
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(RT_Mean ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = RT_Mean ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_RT_Mean = mean(RT_Mean, na.rm = TRUE),
                      std_RT_Mean = sd(RT_Mean, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_RT_Mean, std_RT_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(RT_Mean ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_RT_iso = mean_RT_Mean_isolum__to_bckgrd,
         SD_RT_iso = std_RT_Mean_isolum__to_bckgrd,
         M_RT_off = mean_RT_Mean_offset_to_bckgrd,
         SD_RT_off = std_RT_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_RT_iso, SD_RT_iso, M_RT_off, SD_RT_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("RT | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

**Hitrate** ~ **luminance**

<br> 

```{r lme_HR_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# Hitrate
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(Hitrate ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = Hitrate ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_HR_Mean = mean(Hitrate, na.rm = TRUE),
                      std_HR_Mean = sd(Hitrate, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_HR_Mean, std_HR_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(Hitrate ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_HR_iso = mean_HR_Mean_isolum__to_bckgrd,
         SD_HR_iso = std_HR_Mean_isolum__to_bckgrd,
         M_HR_off = mean_HR_Mean_offset_to_bckgrd,
         SD_HR_off = std_HR_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_HR_iso, SD_HR_iso, M_HR_off, SD_HR_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("Hitrate | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

**FArate** ~ **luminance**

<br> 

```{r lme_FAR_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# FArate
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(FA_proper_rate ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = FA_proper_rate ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_FAR_Mean = mean(FA_proper_rate, na.rm = TRUE),
                      std_FAR_Mean = sd(FA_proper_rate, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_FAR_Mean, std_FAR_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(FA_proper_rate ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_FAR_iso = mean_FAR_Mean_isolum__to_bckgrd,
         SD_FAR_iso = std_FAR_Mean_isolum__to_bckgrd,
         M_FAR_off = mean_FAR_Mean_offset_to_bckgrd,
         SD_FAR_off = std_FAR_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_FAR_iso, SD_FAR_iso, M_FAR_off, SD_FAR_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("FA-rate | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))


```

**d-prime** ~ **luminance**

<br> 

```{r lme_dprime_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# d-prime
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(d_prime ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = d_prime ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_d_Mean = mean(d_prime, na.rm = TRUE),
                      std_d_Mean = sd(d_prime, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum, 
                                values_from = c(mean_d_Mean, std_d_Mean), 
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(d_prime ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_d_iso = mean_d_Mean_isolum__to_bckgrd,
         SD_d_iso = std_d_Mean_isolum__to_bckgrd,
         M_d_off = mean_d_Mean_offset_to_bckgrd,
         SD_d_off = std_d_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_d_iso, SD_d_iso, M_d_off, SD_d_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("d-prime | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

**c criterion** ~ **luminance**

<br> 

```{r lme_c_lum, fig.show = "hide", warning = FALSE, fig.height=4, fig.width=10}
# d-prime
dat2plot_all %>%
  nest() %>%
  mutate(
    stats = map(data, ~ broom::tidy(t.test(c ~ colorlum, data = ., paired = FALSE))),
    t_test_bf = map(data, ~ extractBF(ttestBF(formula = c ~ colorlum, data = ., iterations = num.iter, rscale = sqrt(2)/2))),
    meanval = map(data, ~ .x %>%
                    group_by(colorlum) %>%
                    summarise(
                      mean_c_Mean = mean(c, na.rm = TRUE),
                      std_c_Mean = sd(c, na.rm = TRUE)
                    ) %>%
                    pivot_wider(names_from = colorlum,
                                values_from = c(mean_c_Mean, std_c_Mean),
                                names_sep = "_")
    ),
    cohens_d = map(data, ~ rstatix::cohens_d(c ~ colorlum, data = ., paired = FALSE))
  ) %>%
  unnest(cols = c(stats, cohens_d, t_test_bf, meanval))%>%
  mutate(BF10 = bf, BF01 = 1/bf, 
         M_c_iso = mean_c_Mean_isolum__to_bckgrd,
         SD_c_iso = std_c_Mean_isolum__to_bckgrd,
         M_c_off = mean_c_Mean_offset_to_bckgrd,
         SD_c_off = std_c_Mean_offset_to_bckgrd,
         diff=estimate,
         CohensD = effsize, t.value=statistic, df = parameter)%>%
  dplyr::select(M_c_iso, SD_c_iso, M_c_off, SD_c_off, diff, t.value, df, p.value, CohensD, BF10, BF01)%>%
  # mutate(p.value = p.adjust(p.value, method="holm")) %>% # none, holm
  # mutate(p.value = p.adjust(p.value, method="none")) %>% # none, holm
  ungroup()%>%
  mutate(
    p.value = cell_spec(ifelse(round(p.value,4)<.001,"< .001",round(p.value,4)), 
                        color = ifelse(is.nan(p.value),"blue", ifelse(p.value < .05, "green", "red")),
                        bold = ifelse(is.nan(p.value),F, ifelse(p.value < .05, T,F)),
                        align = "center")
  ) %>%
  kable(escape = F, digits = c(3,3,3,3,3,3,3,3,3), 
        caption = c("criterion | modulation by stimulus display group (isolum vs lum offset) | t-tests of difference")) %>%
  kable_styling("striped", full_width = T, bootstrap_options = c("striped", "hover", "condensed", "responsive",font_size = 8))
```

